\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-11-18 manuscript/ms_MicroMeso.Rnw
new models commit and results

<<echo=FALSE,results=tex>>=
library(xtable)
growthSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/growthClimateContributionTable.csv")
survivalSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/survivalClimateContributionTable.csv")
colonizationSSRTable <- read.csv("../montana/quadBM/vitalRateRegressions/finalModels/colonizationClimateContributionTable.csv")

growthSSRTable[,3:6] <- apply(X = growthSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})
survivalSSRTable[,3:6] <- apply(X = survivalSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})
colonizationSSRTable[,3:6] <- apply(X = colonizationSSRTable[,3:6], MARGIN = 2, FUN = function(x){round(x, digits = 2)})

growthSSRTable$Species <- as.character(growthSSRTable$Species)
survivalSSRTable$Species <- as.character(survivalSSRTable$Species)
colonizationSSRTable$Species <- as.character(colonizationSSRTable$Species)

allTableQBM <- rbind(c("Growth", rep("", times=5)), growthSSRTable, 
                     c("Survival", rep("", times=5)), survivalSSRTable, 
                     c("Colonization", rep("", times=5)), colonizationSSRTable) 
colnames(allTableQBM) <- c("", "N", "Constant model", "Climate model", "Full model", "Contribution of climate covariates")

print(xtable(allTableQBM, align=c("l", "l", "l", "l", "l", "l", "X"), 
             caption="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). The values are residual deviance. Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value."), 
      tabular.environment="tabularx", caption.placement="top",
      width="\\textwidth", include.rownames=FALSE)
@

>>>>

<<echo=FALSE,results=tex>>=
library(xtable)
deviance <- data.frame(VitalRate = c("Growth", "Survival", "Colonization"),
                       ConstantModel = rep(NA,3),
                       ClimateModel = rep(NA,3),
                       FullModel = rep(NA,3),
                       ClimateContribution = rep(NA,3))
deviance$FullModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDeviance.csv")[,2],2)
deviance$ClimateModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDevianceCLIMATE.csv")[,2],2)
deviance$ConstantModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDevianceCONSTANT.csv")[,2],2)
deviance$ClimateContribution[1] <- with(deviance[1,], (ClimateModel-ConstantModel)/(FullModel-ConstantModel))
deviance$ClimateModel[2] <- round(read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalDeviance.csv")[,2],2)
deviance$ConstantModel[2] <- round(read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalDevianceCONSTANT.csv")[,2],2)
deviance$ClimateModel[3] <- round(read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationDeviance.csv")[,2],2)
deviance$ConstantModel[3] <- round(read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationDevianceCONSTANT.csv")[,2],2)
deviance$ClimateContribution[2:3] <- with(deviance[2:3,], (ConstantModel-ClimateModel)/(ConstantModel))

colnames(deviance) <- c("Vital Rate", "Constant model", "Climate model", "Full model", "Contribution of climate covariates")

print(xtable(deviance, align=c("l", "l", "l", "l", "l", "X"), 
             caption="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution for growth is defined as: (Climate model - Constant Model)/(Full model - Constant model). The contribution for survival and colonization, where we could not estimate a full model with year random effects, is defined as: (Constant Model - Climate Model)/Constant Model. The values are model deviance estimated from the `coda' package in R."), 
      tabular.environment="tabularx", caption.placement="top",
      width="\\textwidth", include.rownames=FALSE)
@

### 2014-11-18 manuscript/ms_MicroMeso.tex
new models commit and results

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Sun Oct 26 18:09:01 2014
\begin{table}[ht]
\centering
\caption{The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). The values are residual deviance. Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value.} 
\begin{tabularx}{\textwidth}{lllllX}
  \hline
 & N & Constant model & Climate model & Full model & Contribution of climate covariates \\ 
  \hline
Growth &  &  &  &  &  \\ 
  BOGR & 213 & -881.25 & -881.25 & -938.35 & 0 \\ 
  HECO & 171 & -1365.35 & -1372.06 & -1381.61 & 0.41 \\ 
  PASM & 217 & -2107.02 & -2116.98 & -2164.8 & 0.17 \\ 
  POSE & 197 & -1503.69 & -1502.32 & -1551.44 & -0.03 \\ 
  Survival &  &  &  &  &  \\ 
  BOGR & 218 & 44.62 & 44.62 & 44.53 & 0 \\ 
  HECO & 179 & 51.21 & 51.21 & 51.01 & 0 \\ 
  PASM & 221 & 40.14 & 40.14 & 40.51 & 0 \\ 
  POSE & 204 & 46.41 & 46.41 & 46.25 & 0 \\ 
  Colonization &  &  &  &  &  \\ 
  BOGR & 29 & 38.32 & 39.24 & 44.53 & 0.15 \\ 
  HECO & 68 & 75.78 & 75.78 & 51.01 & 0 \\ 
  PASM & 26 & 32.35 & 32.35 & 40.51 & 0 \\ 
  POSE & 43 & 54.05 & 54.05 & 46.25 & 0 \\ 
   \hline
\end{tabularx}
\end{table}
% # <<echo=FALSE, fig=TRUE,height=3,width=8.5 >>=
% # library(ggplot2)
% # plotD <- data.frame(Species = rep(growthSSRTable$Species, 3),
% #                     Model = rep(c("Growth", "Survival", "Colonization"), each=4),
% #                     Contribution = c(growthSSRTable[,6],
% #                                      survivalSSRTable[,6],
% #                                      colonizationSSRTable[,6]))
% # ggplot(plotD, aes(x=Species, y=Contribution))+
% #   geom_bar(stat="identity")+
% #   facet_grid(.~Model)
% # @

>>>>

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Tue Nov 18 09:15:14 2014
\begin{table}[ht]
\centering
\caption{The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution for growth is defined as: (Climate model - Constant Model)/(Full model - Constant model). The contribution for survival and colonization, where we could not estimate a full model with year random effects, is defined as: (Constant Model - Climate Model)/Constant Model. The values are model deviance estimated from the `coda' package in R.} 
\begin{tabularx}{\textwidth}{llllX}
  \hline
Vital Rate & Constant model & Climate model & Full model & Contribution of climate covariates \\ 
  \hline
Growth & -5566.24 & -5735.32 & -6167.98 & 0.28 \\ 
  Survival & 171.55 & 170.37 &  & 0.01 \\ 
  Colonization & 203.98 & 193.65 &  & 0.05 \\ 
   \hline
\end{tabularx}
\end{table}
% # <<echo=FALSE, fig=TRUE,height=3,width=8.5 >>=
% # library(ggplot2)
% # plotD <- data.frame(Species = rep(growthSSRTable$Species, 3),
% #                     Model = rep(c("Growth", "Survival", "Colonization"), each=4),
% #                     Contribution = c(growthSSRTable[,6],
% #                                      survivalSSRTable[,6],
% #                                      colonizationSSRTable[,6]))
% # ggplot(plotD, aes(x=Species, y=Contribution))+
% #   geom_bar(stat="identity")+
% #   facet_grid(.~Model)
% # @
